A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-26 0_reviewer_response.tex

The following explains the formatting using in this response to reviewers:

\Que{Example text by reviewer.}
\Ans{Example response.}
\paper{New section name}{
Remaining text, followed by 
\revise{outdated text in manuscript}{new text in manuscript}
\revisepar{
Old paragraph which might contain various i.e. multiple lines, which makes the LaTeX macro for strikout text fail, because the soul package doesn't work well enough for our purposes.
}
{Revised paragraph is better.}
}
\todo{Comment for us internally (should be removed before this letter is sent).}
\commits{123commit-hash}

\section{Reviewer 1}
\Summary{
Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed. 
}
\Ans{
We agree with this summary, although it does not stress the contribution of a novel beading scheme in the framework which improves on the state of the art.
We have made various changes to highlight those as separate contributions.
}

%\stepcounter{question}
\Que{
Could the authors provide a mathematical foundation for the relationship between the underfill/overfill areas and the allowed variation of bead width?
I believe the proposed beading scheme can reduce the underfill/overfill areas somehow.
But we still lack a mathematical theory to guide the design.
}
\Ans{
The relationship between under-/overfill and bead widths can be split into several components:
\begin{enumerate*}
\item depending on the feature size
\item depending on the change in feature size
\item depending on the topology
\end{enumerate*}
.
In the first case we consider a part with a constant feature size, in the second we consider the rate of change of feature size and in the third we consider the influence of 3-way intersections.

@@

[\dots]

\revise{We presented}{Compared to the state of the art,} the inward distributed beading scheme
\revise{It}{} reduces the amount of beads with a width deviating extremely from the preferred bead width \revise{}{by changing the width of several beads near the center instead of only the center-most bead}.
\revise{, and thus it is}{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
which in turn is helpful to efficiently simulate an FDM manufactured part.
\revise{
Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.
}{}
}

\subQue{
From Figs.~1b and 1c, we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
}\label{widening_question}
\Ans{
Note that this is not a limitation of the approach, but a consequence of the default parameters which had been chosen.

We have now introduced a new parameter in the widening meta-scheme which can be used specifically to tune the minimal diameter starting from which we generate a toolpath.
This minimum feature size is now used in the new computational test results and in Fig.~1.

We have also changed the example shape of Fig.~17 (old Fig.~16, reproduced here in \cref{visualized_accuracy}) to include a pointy wedge shape similar to Fig.~1.
}
\commits{
%a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13 
d3fe6c86ee887da0e33fefdc43a83d014bc6047b 
0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f 
9281d8ae7350539102be0ead7b2ffc611591d2b4 % fix widening figure
a88ccd3309aef1233ed00ce9f22b244fe64668f4 %  introduce shell meta-scheme and replace widening figure with widening+shell figure
8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to widening + shell fig
ca322806c80ddc82c6f0c01d9ea5096b37ffcf8e % use smae rmin and N=2 in statistics
}
\paper{1. Introduction}
{
[See \cref{intro_wedge} here.]
}
\begin{figure}\centering
\setlength{\figwidth}{.9\mycolumnwidth}
\setlength{\figwidthTwo}{.05\mycolumnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicated in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}
\label{intro_wedge}
\end{figure}

@@

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e. \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e. the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

\revise{It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.}
{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline accuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
%{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
%While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
\revise{However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.}{} % _
Furthermore, \revise{from \cref{smoothness} }{}we find that compared to evenly distributed, the inward distributed scheme produces \revise{smoother toolpaths overall}{less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.
Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes\revise{}{, while incurring little to no extra print time}. 
}

@@

\Que{
More generally, the technique seems to effectively be a variable offset scheme, but there is little discussion about what is known about variable offsets. 
}
\Ans{
Indeed the locations of the junctions in the toolpaths are at variable offsets from the outline, but that doesn't make our framework a variable offset scheme, because the junction locations are determined both by the radius in the central regions and the location of the outline.
Computing the same toolpaths using some variable offset scheme would still require the computation of the radial distances in central regions and relate those to outline locations, which means that we would still need to use the skeleton.
Therefore a variable offset scheme is not an alternative to our framework.

We have not found any variable offset scheme literature which is specifically on toolpath generation, so it wouldn't fit in the related work section.
The method section, however, doesn't go into variable offset schemes because offset schemes apply offset values given at the outline, while our framework principally relates the outline and the skeleton.
}

\Que{
Moreover, the proposed technique seems to rely on rather accurate control of the width w of the deposited material, but it is not clear whether such control is achievable in practice. 
}\label{s5_prints}
\Ans{
On the contrary,
the proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evenly distributed schemes exhibit less variation than the state-of-the-art centered technique.
See Fig.~18d (old Fig.~17b, \cref{widthHistogram} here).

@@

\Que{
Finally, the examples provided depict the results obtained by the authors by "emulating" other techniques, but not with the actual results produced by the other techniques. While the reason behind this choice is easy to guess, it weakens the effectiveness of the claims. Adding careful discussions/extensions to support these questions would make the paper stronger.
}
\Ans{
We've added a paragraph to section~5.4~Limitations, which discusses these emulation limitations.
}
\commits{
639dccad8e97fa1f0bdbb28e16b64f587572792d % paragraph in limitations
}
\paper{5.4 Limitations}
{
\revise{}{
Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
}
}

\section{Reviewer 3}
\Summary{
Paper is well written. It is mostly easy to follow but overall, I find the the contributions somewhat incremental and the motivation not convincing. The paper mostly feels like a technical report. I am not sure if the methods overall teach enough to the researchers in the field to open up new research possibilities. My specific comments are below: 
}
\Ans{
Thank you for your feedback.

}

\Que{
The title is a little misleading that the presented approach may be used for general “Additive Manufacturing”. However, my understanding from the text is that it is designed particularly for FDM. I believe it is important to highlight this in the title. Otherwise, there should be enough evidence to prove that it can be applied to other kinds of printing processes, such as SLS, SLA, DMLS etc. 
}
\Ans{
The title has changed.
}
\commits{
64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0
1935689874235a6c1d5b8f0fed725afa53804935 % don't introduce only one strategy for FDM only
}
\paper{Title}{
A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}
}
\paper{1. Introduction, bullet list}{
A specific beading scheme \revise{for FDM printing}{} which [\dots]
}

### 2020-01-28 0_reviewer_response.tex

\section*{Formatting of this document}
This document contains the reviewer feedback on the first submission, our response to that feedback and the changes we made to arrive at the current submission.
When referring to figure numbers we clearly indicate whether we are referring to a figure in this document (`here'), in the first submission (`old') or in the current submission (`now').
References numbers in the textual changes reproduced here do not correspond with the reference numbers in the actual manuscript.

The following explains the formatting using in this response to reviewers:

\Que{Example text by reviewer.}
\Ans{Example response.}
\paper{New section name}{
Remaining text, followed by 
\revise{outdated text in manuscript}{new text in manuscript}
\revisepar{
Old paragraph which might contain various i.e. multiple lines, which makes the LaTeX macro for strikout text fail, because the soul package doesn't work well enough for our purposes.
}
{Revised paragraph is better.}
}
\todo{Comment for us internally (should be removed before this letter is sent).}
\commits{123commit-hash}

\section{Reviewer 1}
\Summary{
Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed. 
}
\Ans{
Thank you.
We have addressed the comments, and have clarified our contributions.
}

@@

\Que{
Is this approach generalizable to sparse infill? It is very common in FDM to use a sparse infill and only use dense fill on surface regions.
}
\Ans{
The goal of sparse infill is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
See our response to question~\ref{outline_question}.
}

\Que{
If this is used for outer surface, what are the implications on the surface quality in comparison to other approaches? 
}
\Ans{
The visual quality in terms of a homogenous surface are discussed in the section on the new printing results.
See our response to question~\ref{s5_prints}.
}

\Que{
I think Fig.~13 should be replaced with a table. 
}
\Ans{
Indeed. Done.
}
\commits{735762b1e7daf31ae4465bf288ef867ded7da095}
% commit only now shows table

\Que{
In text, some references are missing, such as first sentence of “Outer bead” paragraph in Section~4 (Moesen et al [?]), first sentence of “Constant bead count” (Ding et al [?]) paragraph in Section~4 etc. 
}
\Ans{
We cannot reproduce this typesetting bug, and will pay attention to this in future proofreading.
}

### 2020-01-28 0_reviewer_response.tex

We have made some improvements on the abstract.
\commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
\paper{Abstract}{
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
}

We added an url to the open source implementation.
\commits{
ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a
}
\paper{6. Conclusion}{
\revise{}{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}
}

### 2020-01-28 0_reviewer_response.tex

The old photos (old Fig. 18, here \cref{prints_old}) of our print results already showed that adaptive width control is possible up to an admittedly insufficient extent.

Because it was insufficient, we have now developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: \emph{back pressure compensation}.
We show the results of back pressure compensation in a new figure (Fig. 15, reproduced here in \cref{back_pressure_compensation}) which clearly shows the achieved variance in bead width.

All paragraphs on the physical realization, i.e. on linear advance and its limitations and on gcode limitations, have been assembled together and moved to 5.1. Fabrication.
Because the print time statistics use our back pressure compensation approach we moved the fabrication results to before the statistical analysis.
}

\commits{
%3d7238e2787f17c4cff63804eb4b84439ff85f1b  % initial printing results section~5.2
%b5abdd980240cd4ca964ed0f4751c207baa09b85 % move 5.5 to 5.2
a0e98d1079b3ab3b262908ea056939813fc49c73 % move 5.2 to 5.3 and overhaul
6362bb7f1ff11e15efc6667fc7863ca12a29a8a9 % mention in intro and conclusion
22cb3664ddc722d25e0a73df905100410f8ebf10 444a00a54100e402024335b79265b6900017bc1d ab38e07c84b6e62dc028d224b7a57bba9239552f cb3325a9cf00457fab5f1bdc5d29f1d178de4e35% S5 prints
d375878a8a6d01c53436aeb9c473dbedd8f3edcf % prints discussion
125162ad9878c0fb5a054f1bab34aa7b1353b86c % better var width test figure
34e923fbf4c2ad45bf2dd0a03ef70d4a714b4b0b % lil comma (x2)
1b7bb61648b97b8084ca8817aa457bde2c91e1b3 % lil: explain unexplained math symbol 
}
\paper{Abstract}
{
We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd
\revise{}{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
}
\paper{5.1.2 Printing results}
{
\revisepar{
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
%}{}
\par
%\revisepar{
The prints are shown in \cref{prints_old}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
}{}

@@

We removed the angles graph of old Fig.~17e.
The effect that transitioning reduces sharp angles in the toolpath is apparent and doesn't require empirical proof.

We fixed a mistake when performing the statistical analysis. In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme. The extrusion width statistics figure (now Fig.~18d, old Fig.~17b, \cref{widthHistogram} here) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.

We changed the width histogram calculation so that we use accurate statistics instead of sampling the width along the path.
\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
\paper{5.2.2 Uniformity}
{
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
}

We have made some improvements on the abstract.
\commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
\paper{Abstract}{
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd
\revise{}{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
}
